An Exegesis of Ontological Hermeneutics

### 2022-10-29 responseToReviews/response_to_reviewers.tex

\documentclass[12pt]{report}
\usepackage{color,soul}
\usepackage{subcaption,wrapfig,graphicx,booktabs,fancyhdr,amsmath,amsfonts}
\usepackage{cite,bm,amssymb,amsthm,url,multirow,times,enumitem,comment}
\usepackage{mathtools,siunitx,tikz}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\newcommand{\vb}{\boldsymbol}
\newcommand{\vbh}[1]{\hat{\boldsymbol{#1}}}
\newcommand{\vbc}[1]{\check{\boldsymbol{#1}}}
\newcommand{\vbb}[1]{\bar{\boldsymbol{#1}}}
\newcommand{\vbt}[1]{\tilde{\boldsymbol{#1}}}
\newcommand{\vbs}[1]{{\boldsymbol{#1}}^*}
\newcommand{\vbd}[1]{\dot{{\boldsymbol{#1}}}}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\by}{\times}
\newcommand{\tr}{\mathsf{T}}
\newcommand{\sfrac}[2]{\textstyle \frac{#1}{#2}}
\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}
\newcommand{\sinc}{\text{sinc}}
\renewcommand{\equiv}{\triangleq}
\newcommand{\cnr}{C/N_0}
\newcommand{\sgn}{\text{sgn}}
\renewcommand{\Re}{\mathbb{R}}
\renewcommand{\Im}{\mathbb{I}}
\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

\topmargin = 0 mm 
\oddsidemargin = -1 mm 
\evensidemargin = -1 mm
\headheight = 0 mm 
\headsep = 8 mm 
\textheight = 220 mm 
\textwidth =170 mm 
\parindent = 0 mm
\parskip = 4 mm

\begin{document}

\section*{Reviewer 1}
\subsection*{General Comments:}

{\textit{This is a very nice, thorough piece of work that develops on the
    authors' previous contributions to GNSS spoofing detection. The paper
    expands on the previously introduced ``sandwich'' detector, which utilises
    both overall power level monitoring and per channel correlation distortion
    monitoring to classify each received signal as belonging to one of the 4
    classes: nominal, multipath, jammed, or spoofed.}}

{\textit{The development is clear and the text is well structured and well
    written and deserves to be published with some largely minor
    modifications.}}

{Thank you for your assessment and helpful comments.}

\subsection*{Suggested Improvements:}

{\textit{One area that could do with some clarification relates to
      Section IV A -
Received Power Level Measurement, in particular Eqn
      (5). In the preceding
development leading up to this section the
      authors have considered a single
signal only, which is both appropriate
      and simplifies the notation. However,
when considering the overall
      power in the receiver, the chosen notation and
description becomes
      somewhat convoluted. I think it would clarify the matter
here to
      introduce the total power as the sum of the power from all
      satellites
(and all signals within the L1 band from all satellites),
      the power from all
interference sources (jammers/spoofers etc) and the
      cross terms (between
satellites, between interferers and between
      satellites and interferers). In
this manner it is not necessary to
      decide whether an interferer should be
classified as part of the
      MAI. With this fuller notation, needed only for the
power level
      measurement, it would be clear where each contribution to the
overall
      measured power comes from.}}

  { This is a good suggestion.  We have adopted it fully in the revised
    Section IV.  The new Eq. (6) expresses the combined signal as the
    summation of all authentic and interference signals, plus noise.  $P_k$ is
    now defined in terms of this combined signal (cf. Eq. (7)), and the
    mean of $P_k$ (in linear units) is expressed as a sum of constituents,
    including cross-terms between authentic and interference signals
    (cf. Eq. (8)).  No cross-terms between interferers themselves is
    necessary in Eq. (8), as interferers are assumed to be mutually
    independent, as now explained in the paragraph just before (8).}

{\textit{In addition, I would argue that Eqn (6) is not strictly
      correct, as the right
hand side represents not the Power Spectral
      Density due to MAI, but rather the
total power due to MAI. Indeed the
      right hand side is the closed form solution
of the so-called spectral
      separation coefficient for BPSK(1) assuming infinite
transmit and
      receive bandwidths. Using Eqn (6) as is would greatly over
estimate the
      contribution of MAI to total received power.}}

  {We agree, and are grateful that you caught this error.  The revised
    expression for $P_k$ (Eqs. (7) and (8)) does not attempt approximation via
    $M_0$.  The earlier approach was equivalent to the current (correct)
    approach when $W_P = 3/(2\tau_c)$, but, as $W_P$ is assumed larger than
    $3/(2\tau_c)$, our former approach exaggerated the contribution of
    multi-access signals to $P_k$.  We have corrected our code and re-run the
    paper's simulations and tests against empirical data.}

{\textit{This leads to my final concern with this section: I don't really
      see how matched
power spoofing can lead to a total power delta of
      approximately 2 dB in a 2 MHz
bandwidth as shown in Fig. 4. By my
      calculation this would require an average
C/No of about 50 dB-Hz from
      approximately 20 satellites simultaneously.
I presume the large delta
      in Fig. 4 is largely due to the RF image energy
introduced by the
      spoofer. My concern then is that this same spoofer has been
used in the
      live data experiments also. Is this justifiable? Is it likely that
such
      a large amount of in-band noise would be generated by a "real world"
      spoofer?
}}

  We have revisited our empirical measurements and our calculations and can
  re-affirm the $\sim$2 dB uptick in the 2-MHz bandwidth at the beginning of
  spoofing in TEXBAT Scenario 3.  We were also surprised at the size of the
  increase.  It can be explained by noting that, for the high-quality antenna
  (Trimble Geodetic Zephyr II) and receiver (a 16-bit National Instruments
  front end) in question, the total authentic power in the 2-MHz bandwidth
  under nominal (clean) conditions was measured to be approximately -142 dBW.
  This is the combined power of $M_s + 1 = 12$ authentic GPS L1 C/A signals
  (plus a small amount of power from GPS L1(P)).

  This is a surprisingly large combined power.  Assuming a noise floor of -204
  dBW/Hz (thermal noise only, no multi-access noise), the total noise power in
  a 2-MHz bandwidth would be $63 - 204 = -141$ dBW.  Thus, the combined power
  of the authentic signals (and mild multipath) for this antenna/receiver
  combination is nearly equal to the total noise power in band.  One can
  verify this by examining the new Fig. 3, which shows the nominal (clean)
  spectrum in dark gray.  Selective integration of the spectrum reveals that
  the power in the center 2 MHz band is indeed twice that of the power in a 2
  MHz band of the noise floor (which one can approximate by centering a 2 MHz
  band at -4 MHz).

    The upshot of this is that, \emph{relative to the noise floor alone} (no
    multi-access interference), of the 12 authentic signals, there are two
    signals with $C/N_0 \approx 55$ dB-Hz (PRNs 13 and 23), two others with
    $C/N_0 \approx 53$ dB-Hz (PRNs 3 and 16), and three others above
    $C/N_0 \approx 50$ dB-Hz, with many of the remaining signals in the mid-
    to high-40 dB-Hz range.  Note that the \emph{measured} $C/N_0$ values are
    approximately 3 dB lower than this due to multi-access interference. (In a
    typical receiver, measured $C/N_0$ is actually $C/(N_0 + M_0)$.)

    Note also that, for TEXBAT Scenario 3, $\eta_i = 1.3$ for all $i$.  Thus,
    although Scenario 3 is advertised as a ``matched power'' scenario, it is
    only approximately so.  A truly matched scenario would have $\eta_i = 1$
    for all $i$.

    The reviewer is correct that some wideband quantization noise and aliasing
    due to the rudimentary RF front-end enters the 2 MHz band around L1 for
    TEXBAT Scenario 3.  But the power of such noise is small compared to the
    power in the spoofing signals of Scenario 3.  The quantization and
    aliasing noise does tend to make TEXBAT Scenarios 1-6 easier to detect
    than a more sophisticated spoofing attack would be (because they have
    slightly higher power).  But TEXBAT Scenario 7 does not suffer from such
    quantization and aliasing noise, nor do any of the Monte-Carlo-simulated
    scenarios against which the PD detector was tested.

    In any case, to avoid any confusion, and to avoid distracting the reader
    with excuses for the rudimentary front end used in TEXBAT Scenarios 1
    through 6, we have changed Figs. 3 and 4 to reflect the spoofing scenario
    from TEXBAT Scenario 7, which is free of aliasing or quantization noise.
    We have also re-drawn the nominal (clean) plots to make them clearer.

    Furthermore, to call attention to the extra noise in TEXBAT Scenarios 2
    through 6, we have modified the second paragraph of VII.A to read

    \begin{quotation}
      Note that {\tt tb2}--{\tt tb6} exhibit a modest amount of quantization
      and aliasing noise that makes them easier to detect than would be
      expected based on this paper's models, whereas {\tt tb7} is free from
      such extraneous noise.  {\tt tb7} is also special in that the spoofer
      exercises control of $\Delta \theta$, permitting nulling, as described
      in Section V-A, in the early stages of the attack.  In all other TEXBAT
      recordings, the spoofer controlled $\eta$ and $\Delta \tau$ but left
      $\Delta \theta$ at an arbitrary constant value ({\tt tb3}, {\tt tb4},
      and {\tt tb6}) or allowed it to ramp consistent with the pull-off rate
      ({\tt tb2} and {\tt tb5}).
    \end{quotation}

{\textit{Another area that could be made clearer is that the aim of
      this paper is not
so much to detect spoofing per se, but rather to
      detect a carry-off attack.
Thus H2 is the hypothesis that a carry-off
      attack is underway. This pre?supposes
that the receiver is initially
      tracking true GPS signals. This is a small point
but it is important to
      be clear on this.}}

 We agree that this clarification is warranted, and have modified the
  abstract, the introduction, and the conclusion to make clear that our
  spoofing detection applies to carry-off-type attacks.

\subsection*{Minor Comments:}

{\textit{Introduction: "... no civil GNSS signals yet incorporate cryptographic modulation...
" \\
      perhaps better to say "... no open civil GNSS signals ..." as the
      Galileo
Commercial Service is indeed a civil GNSS signal incorporating
      cryptographic
modulation.}}

  {We have incorporated this clarification in our revised manuscript.}

{\textit{P. 11: Under H2: Spoofing. Here you do not permit advance of the
      spoofed signal
with respect to the authentic signal, why?  Also, you
      state that spoofing where
the time difference exceeds two chips "is
      more properly classified as jamming".
I would argue that under certain
      circumstances this could well be classified
as very successful
      spoofing.}}

   Thank you for pointing this out.  We unwittingly left off the absolute
    value bars around $\Delta \tau$ here and in the description of $H_3$.  We
    have now fixed this, indicating that spoofing can be either advanced or
    delayed wrt the authentic signal.  We have also modified the text to
    justify our classification of spoofing as jamming when $|\Delta \tau|$ is
    sufficiently large:

    \begin{quotation}
      These bounds make sense because the spoofing signal must be at least as
      powerful as the authentic signal for reliable spoofing, and because
      spoofing whose $|\Delta \tau|$ value exceeds $\Delta \tau_1 = 2\tau_c$
      is no longer classified as carry-off-type spoofing, since the
      interference is uncorrelated with the authentic signal.  Instead, for
      $|\Delta \tau| \geq \Delta \tau_1$, the attack is classified as jamming.
    \end{quotation}

    We have left the assumed distribution of $\Delta \tau$ under $H_2$ as it
    was, since the worst case attack occurs when the spoofer mimics multipath.

{\textit{Figure 10 ? there's a floating exclamation mark (!) after
      the figure ? most
likely a TeX float placement command gone
      wrong...}}

  {{We have fixed this.  You were correct that it was a placement command
        gone wrong.}}

\section*{Reviewer 2}
\subsection*{Suggestions for Improvement:}

{\textit{The paper is generally well written and organized; however, the
      notation used is sometimes distracting. The proposed power-distortion
      detector is very interesting in that it can detect both high-power and
      low-power spoofing attempts. The authors acknowledge that the monitor is
      ineffective in cases where the spoofer is able to block or null the
      authentic GPS signals (which is difficult to accomplish). However, in
      the results section, while discussing Table 3, it is stated that the
      proposed detector is most effective during the initial spoofer
      pull-off. Beyond a certain point, the distortion will subside, and the
      monitor's effectiveness would decrease.}}

   Agreed.  We have modified the paper's abstract, introduction, and
    conclusion to emphasize the fact that its spoofer detection is designed to
    work for carry-off spoofing attacks; in particular, during the initial
    stages of a carry-off attack when distortion remains significant.

{\textit{It would be interesting to see how very slow spoofer pull-off
      would affect the monitor, and what the resulting minimum detectable
      error would be. It appears unlikely that the proposed monitor can be
      completely fooled by a slow pull-off rate. However, the experimental
      results section does not mention details regarding the spoofer's
      pull-off rate. If it is very slow, is seems possible that the detector
      would initially classify the spoofing as multipath. Then, beyond a
      certain minimum detectable error, the detector would correctly identify
      the spoofing attempt. It is possible that the reason why results in
      Table 3 show no instances where spoofing is classified as multipath is
      because of a sufficiently quick pull-off rate.}}

   The reviewer is correct that close-in (small $|\Delta t|$),
    low-powered spoofing could fool the PD detector into declaring multipath
    ($H_1$).  However, a slow pull-off would afford the PD detector
    \emph{more} opportunities to observe distortion and declare the attack as
    spoofing than a fast pull-off attack.  We believe that the primary reason
    no empirical spoofing scenarios were mis-classified as multipath is that
    they were all designed to be \emph{effective} spoofing attacks, with
    sufficiently large $\eta$ to effect pull-off of the tracking points.
    Thus, while they were sometimes confused for jamming, their received power
    was too strong to be confused with multipath.

    The three references to TEXBAT data given in Section VII-A offer details
    on the pull-off rates of each attack.  In particular, {\tt tb7} has a
    particularly slow pull-off, whereas {\tt tb2} throuth {\tt tb6} are faster.

\subsection*{Minor Comments:}

{\textit{Variable `C' is used to represent the C/A code, and later used
      to represent the cost function}}

  {{We have modified $C(t)$ to read $C_r(t)$ throughout to avoid this confusion.}}

{\textit{letter 'j' is used to denote the imaginary unit on pg. 5,
      as well as a time index (pg. 7), and parameter space index
      (pg. 22) }}

  {{ Thanks for pointing this out. However, in this context, we do feel that
      the meaning of our notation is clear. That is, $j$ is often used as an
      indexing variable, and we have already used $i$ and $k$ elsewhere in the
      paper. Likewise, either $i$ or $j$ are also traditionally used to
      indicate imaginary components. Given that there is no overlap within the
      same expression, we'd prefer to keep the notation as is in this case.}}

{\textit{ Two different notations for conditional probability are used
      throughout the paper, both the conventional notion, P(A|B), and
      subscript notion, $P_B(A)$. At times, the subscript notion can become
      distracting, because it is used to denote conditional as well as
      marginal distributions (pg. 9 for example). For example, on page 16, the
      notation used for the conditional density of $D_k$, defined as
      $p_{Dk}(x | \theta)$, is confusing because it appears that both
      notations are used simultaneously. Adhering to the conventional notion,
      $P(A|B)$, for conditional probabilities would improve readability, and
      eliminate extraneous definitions (on pg. 8 for example). }}

  {{ Thank you for this suggestion.  We agree and have
        updated our notation in the revision.  $p_\theta(z_k)$ is now written
        as $p(z_k | \theta)$, and $p_i(z_k)$ as $p(z_k | \Theta \in
        \Lambda_k)$.  We have retained the notation $w_i(\theta)$ for
        compactness and because there is no risk of ambiguity. }}

{\textit{When the cost function is introduced on page 8, the
      definition C[i,$\theta$] is puzzling because it is simply defined
      as the cost of choosing hypothesis i, given $\theta$ belonging to
      $\Lambda$ (the entire parameter space). This initially made it
      seem that the cost is uniform across the entire parameter
      space. Later in the paper, section 6 helps clarify the definition
      by showing two different types of cost function. Uniform costs are
      discussed, as well as non-uniform costs, for various cases of
      $\theta$ in $\Lambda_i$. Additional explanation of the cost
      function definition on page 8 would be beneficial. }}

    Thank you for this pointing out this need.  We agree and have added
    the following language around the introduction of the cost function:

        \begin{quotation}
          Let $C[i,{\theta}]$ be the cost of choosing $H_i$ when
          ${\theta} \in \Lambda$ is the actual parameter vector.  Note that
          this function is sensitive to a particular value of $\theta$, which
          makes it more general than one that simply assigns a unform cost for
          choosing $H_i$ when $\theta \in \Lambda_j$.  A later section will
          introduce various embodiments of $C[i,{\theta}]$.
        \end{quotation}

\section*{Reviewer 3}
\subsection*{Suggestions for Improvement:}

{\textit{Figure 2 can be improved by using some 3D effect on the
      correlation functions.}}

   Fig. 2 already includes some features that help the reader view it in
    3 dimensions.  First, it offers a perspective view of a 3D coordinate
    frame in $I$, $Q$, and $\tau$.  Second, in the upper-right inset it allows
    the viewer to appreciate the angular difference between $\xi_{Ak}$ and
    $\xi_{Ik}$ by offering a view along the $\tau$ axis.

{\textit{Please explain why the signal models in section II did not
      include a frequency component. With interference or any strong secondary
      signal, it is possible for the tracking loop to diverge which results in
      tracking frequency error. If the error is sufficiently small, it may
      result in a time varying phase.}}

### 2023-02-07 paper.tex
PL, blocking, and shadowing

\documentclass[10pt,journal,twocolumn]{IEEEtran} % add 'draft' to suppress figures
% Double-spaced, single-column format for IEEE journal submission
% \documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran} 
\usepackage{wrapfig,booktabs,fancyhdr,amsmath,amsfonts,tabularx,numprint}
\usepackage{cite,bm,bbm,amssymb,amsthm,url,multirow,times,enumitem,comment}
\usepackage{mathtools,siunitx,balance,tikz,adjustbox,graphicx,array}
\usepackage[font=footnotesize]{subcaption}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\newcommand{\vb}{\boldsymbol}
\newcommand{\vbh}[1]{\hat{\boldsymbol{#1}}}
\newcommand{\vbc}[1]{\check{\boldsymbol{#1}}}
\newcommand{\vbb}[1]{\bar{\boldsymbol{#1}}}
\newcommand{\vbt}[1]{\tilde{\boldsymbol{#1}}}
\newcommand{\vbs}[1]{{\boldsymbol{#1}}^*}
\newcommand{\vbd}[1]{\dot{{\boldsymbol{#1}}}}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\by}{\times}
\newcommand{\tr}{\mathsf{T}}
\newcommand{\sfrac}[2]{\textstyle \frac{#1}{#2}}
\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}
\newcommand{\sinc}{\text{sinc}}
\newcommand{\define}{\triangleq}
%\newcommand{\define}{\coloneqq}
\newcommand{\cnr}{C/N_0}
\newcommand{\sgn}{\text{sgn}}
\renewcommand{\Re}{\mathbb{R}}
\renewcommand{\Im}{\mathbb{I}}
\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\brm}[1]{\bm{\text{#1}}}
\newcommand{\round}[1]{\ensuremath{\lfloor#1\rceil}}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

@@

@@

\author{
  \IEEEauthorblockN{Gandalf the White\IEEEauthorrefmark{1}, Radagast the
    Brown\IEEEauthorrefmark{2}, Todd E. Humphreys\IEEEauthorrefmark{1}} \\
  \IEEEauthorblockA{\IEEEauthorrefmark{1}\textit{Department of Aerospace
      Engineering and Engineering Mechanics, The University of Texas at Austin}} \\
  \IEEEauthorblockA{\IEEEauthorrefmark{2}\textit{Department of Elven Lore, The
    University of East Rivendell}}
}

\maketitle

\begin{abstract}
  The abstract is a one-paragraph summary of the whole paper.  Out of respect
  for busy readers, it gets right to the point.  The first 2-3 sentences
  unpack the title and motivate the paper.  The remainder briefly offers
  context (if necessary) and further describes the paper's method, explaining
  how it fills a gap in the existing literature.  The abstract reveals all the
  paper's main results in language that is bold but truthful.

An example for a paper titled ``Deep urban unaided precise GNSS vehicle
positioning'': \\ \\

This paper presents the most thorough study to date of vehicular carrier-phase
differential GNSS (CDGNSS) positioning performance in a deep urban setting
unaided by complementary sensors.  Using data captured during approximately 2
hours of driving in and around the dense urban center of Austin, TX, a CDGNSS
system is demonstrated to achieve 17-cm-accurate 3D urban positioning (95\%
probability) with solution availability greater than 87\%.  The results are
achieved without any aiding by inertial, electro-optical, or odometry sensors.
Development and evaluation of the unaided GNSS-based precise positioning
system is a key milestone toward the overall goal of combining precise GNSS,
vision, radar, and inertial sensing for all-weather high-integrity
high-absolute-accuracy positioning for automated and connected vehicles.  The
system described and evaluated herein is composed of a densely-spaced
reference network, a software-defined GNSS receiver, and a real-time kinematic
(RTK) positioning engine.  A performance sensitivity analysis reveals that
navigation data wipeoff for fully-modulated GNSS signals and a dense reference
network are key to high-performance urban RTK positioning.  A comparison with
existing unaided systems for urban GNSS processing indicates that the proposed
system has significantly greater availability or accuracy.
\end{abstract}

\begin{IEEEkeywords} 
urban vehicular positioning; CDGNSS; low-cost RTK positioning.
\end{IEEEkeywords}

%%% -------------------------- Select preprint or "for submission" version
\newif\ifpreprint
\preprintfalse
%\preprinttrue

\ifpreprint

\pagestyle{plain}
\thispagestyle{fancy}  
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt}
\rfoot{\footnotesize \bf October 2020 preprint of paper submitted for review} \lfoot{\footnotesize \bf
  Copyright \copyright~2020 by Lakhsay Narula \\ and Todd E. Humphreys}

\else

\thispagestyle{empty}
\pagestyle{empty}

\fi

%%% ----------------------------------------------------------------------

\section{Introduction}
In the introduction:
\begin{itemize}
\item {\bf Background:} Set the stage in a compelling way to draw the reader
  in.
\item {\bf Opportunity/Need:} Identify a need or an opportunity.
\item {\bf The status quo:} Review the state of the art.  
\item {\bf Gap:} Mind the gap!  Convince your reader that there is an
  important deficiency (gap) in the existing literature or practice, and that
  your paper will save the day by filling in/bridging this gap.  Otherwise,
  why should your reader take time to read the paper?
\item {\bf Vision:} Invite the reader to imagine the way the world could be if
  only the gap could be bridged.
\item {\bf Contributions:} Clearly enumerate the paper's contributions.
\end{itemize}

What follows is an example introduction taken from
\cite{humphreys2019deepUrbanIts}. \\ \\

\IEEEPARstart{F}{uture} Vehicle-to-vehicle (V2V) and vehicle-to-infrastructure
(V2I) connectivity will permit vehicles to relay their positions and
velocities to each other with millisecond latency, enabling tight coordinated
platooning and efficient intersection management.  More ambitiously, broadband
V2V and V2I enabled by 5G wireless networks will permit vehicles to share
unprocessed or lightly-processed sensor data. \emph{Ad hoc} networks of
vehicles and infrastructure will then function as a single sensing organism.
The risk of collisions, especially with pedestrians and cyclists---notoriously
unpredictable and much harder to sense reliably than vehicles---will be
significantly reduced as vehicles and infrastructure contribute sensor data
from multiple vantage points to build a blind-spot-free model of their
surroundings.

Such collaborative sensing and traffic coordination requires vehicles to know
and share their own position.  How accurately?  The proposed Dedicated Short
Range Communications (DSRC) basic safety message, a first step in V2V
coordination, does not yet define a position accuracy requirement, effectively
accepting whatever accuracy a standard GNSS receiver provides
\cite{kenney2011dedicated}.  But automated intersection management
\cite{fajardo2011automated}, tight-formation platooning, and unified
processing of sensor data---all involving vehicles of different makes that may
not share a common map---will be greatly facilitated by globally-referenced
positioning with sub-30-cm accuracy.

Poor weather also motivates high-accuracy absolute positioning.  Every
automated vehicle initiative of which the present authors are aware depends
crucially on lidar or cameras for fine-grained positioning within their local
environment.  But these sensing modalities perform poorly in low-visibility
conditions such as a snowy whiteout, dense fog, or heavy rain.  Moreover,
high-definition 3D maps created with lidar and camera data, maps that have
proven crucial to recent progress in reliable vehicle automation, can be
rendered dangerously obsolete by a single snowstorm, leaving vehicles who rely
on such maps for positioning no option but to fall back on GNSS and radar to
navigate a snow-covered roadway in low-visibility conditions.  When, as is
often the case on rural roads, such snowy surroundings offer few
radar-reflective landmarks, radar too becomes useless.  GNSS receivers operate
well in all weather conditions, but only a highly accurate GNSS solution,
e.g., one whose absolute errors remain under 30 cm 95\% of the time, could
prevent a vehicle's drifting onto a snow-covered road's soft shoulder.  Code-
and Doppler-based GNSS solutions can be asymptotically accurate (averaged over
many sessions) to better than 50 cm, which may be adequate for digital mapping
\cite{narula2018accurate}, but they will find it challenging to meet a 30 cm
95\% stand-alone requirement, even with modernized GNSS offering wideband
signals at multiple frequencies.

>>>>

\documentclass[12pt]{report} % add 'draft' to suppress figures
% Double-spaced, single-column format for IEEE journal submission
% \documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran} 
\usepackage{wrapfig,booktabs,fancyhdr,amsmath,amsfonts,tabularx,numprint}
\usepackage{cite,bm,bbm,amssymb,amsthm,url,multirow,times,enumitem,comment}
\usepackage{mathtools,siunitx,balance,tikz,adjustbox,graphicx,array}
\usepackage[font=footnotesize]{subcaption}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makeglossaries

 \newcommand{\vb}{\boldsymbol}
\newcommand{\vbh}[1]{\hat{\boldsymbol{#1}}}
\newcommand{\vbc}[1]{\check{\boldsymbol{#1}}}
\newcommand{\vbb}[1]{\bar{\boldsymbol{#1}}}
\newcommand{\vbt}[1]{\tilde{\boldsymbol{#1}}}
\newcommand{\vbs}[1]{{\boldsymbol{#1}}^*}
\newcommand{\vbd}[1]{\dot{{\boldsymbol{#1}}}}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\by}{\times}
\newcommand{\tr}{\mathsf{T}}
\newcommand{\sfrac}[2]{\textstyle \frac{#1}{#2}}
\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}
\newcommand{\sinc}{\text{sinc}}
\newcommand{\define}{\triangleq}
%\newcommand{\define}{\coloneqq}
\newcommand{\cnr}{C/N_0}
\newcommand{\sgn}{\text{sgn}}
\renewcommand{\Re}{\mathbb{R}}
\renewcommand{\Im}{\mathbb{I}}
\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\brm}[1]{\bm{\text{#1}}}
\newcommand{\round}[1]{\ensuremath{\lfloor#1\rceil}}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

@@

\newacronym{PL}{PL}{Path loss}
\newacronym{LOS}{LOS}{Line of sight}
\newacronym{NLOS}{NLOS}{Non-line of sight}

@@

\tableofcontents
\chapter{Path Loss Models}

\gls{PL} models are formulas which allow for modeling the received
power $P_r$ given the transmit power $P_t$, distance $d$, and signal carrier
wavelength $\lambda$. The resulting \gls{PL} is due to signal propagation
through the environment.

\section{Friss Formula}
For a transmitter and receiver spaced $d$ distance apart, the received power
$Pr$ follows:

\begin{align}
  \label{eq:general_PrPt}
  P_r = P_t \frac{1}{4\pi d} A_e
\end{align}

where $A_e = \frac{\lambda}{4 \pi}$ for an omnidirectional antenna and a signal
with a wavelength $\lambda$. Substituting $A_e$ in (\ref{eq:general_PrPt})
provides the Friis Formula, which applies for a wireless channel in a vacuum.
Further adding terms $G_t$ and $G_r$ for the transmit and receive antenna gains,
we reach the generalized Friis formula.

\begin{align}
  \label{eq:friss_formula}
  P_r = \frac{G_t G_r \lambda ^2 P_t}{(4\pi d)^2}
\end{align}

\section{Path Loss Exponent Model}
Since wireless channels exist in environments without a vacuum, a generalized
model is needed to cover a variety of cases. A generalized such model is an
exponential model using the received power formula below.

\begin{align}
  \label{eq:general_exp_PL}
  P_r = P_t G_t G_r K \left[\frac{d_0}{d}\right]^\alpha
\end{align}

The parameter $d_0$ is a unit normalization parameter, usually set to $1$ m. The
parameter $\alpha$ is the \gls{PL} exponent. The parameter $K$ is the nominal
\gls{PL} at $1$ m. Notice when $K = [\frac{\lambda}{4 \pi}]^2$ defined as $K_0$
and $\alpha = 2$, the formula reveals the Friis Formula from
(\ref{eq:friss_formula}).

\chapter{Multipath Effect Modeling}
Other than the natural landscape of the environment, there are other effects
that may further increase \gls{PL}.

\section{Blocking}
Blocking allows for a multi-slope \gls{PL} model. Essentially, the \gls{PL}
model has multiple definitions, and follows each one with a certain probability.
This usually translates to following a certain \gls{PL} for a \gls{LOS} path,
and following another model for the \gls{NLOS} path. A common model for this is
the Exponential Blocking model

\begin{align}
  \label{eq:exp_blocking}
  P_r = \left\{ \begin{array}{ll}
                  PL_{LOS}  & \text{w.p.} ~~~~~~ e^{-d/\beta}  \\
                  PL_{NLOS} & \text{w.p.} ~~~ 1 - e^{-d/\beta} \\
                \end{array}
  \right.
\end{align}

where $\beta$ acts as the mean distance before blocking occurs (i.e. by a building), and the $PL_{LOS}$ and $PL_{NLOS}$ terns are functions for \gls{PL} models.

\subsection*{Blocking example}
Imagine a scenario in which a \gls{LOS} path is in free space and the \gls{NLOS} is modeled as an exponential \gls{PL} with an exponent $\alpha = 2.5$ and a distance of $d = 100$ between the transmitter and receiver. The blocking exponent $\beta = 25$. What does the $SNR = P_r/P_t$ model finalize to if $G = G_t G_r = 1$, $K_{\text{LOS}} = K_{\text{NLOS}} = K_0 = -40$ dB and $d_0 = d_1 = 1$.
\\
\\
Answer:

\begin{align}
  SNR = \frac{P_r}{P_t} = \left\{ \begin{array}{ll}
                                    K_0 \left[\frac{1}{100}\right]^2     & \text{w.p.} ~~~~~~ e^{-100/25}  \\
                                    K_0 \left[\frac{1}{100}\right]^{2.5} & \text{w.p.} ~~~ 1 - e^{-100/25} \\
                                  \end{array}
  \right. \nonumber
  = \left\{ \begin{array}{ll}
              -80 \text{ dB} & \text{w.p.} ~ 0.0183 \\
              -90 \text{ dB} & \text{w.p.} ~ 0.9817 \\
            \end{array}
  \right. \nonumber
\end{align}

\section{Shadowing}
Shadowing is attenuation caused by objects between the transmitter and
receiver that reduce the received signal's power. It is modeled as random and does not depend on the distance of the wireless communication link. By modeling shadowing we account for the constructive and destructive interference cause by the transmitted signal reflecting, diffracting and scattering, the components of which are called multipath components.

The shadowing effect is modeled as lognormal. The received power equation from a \gls{PL} model is simply multiplied with a new variable $\mathcal{X}$, where $x_{\text{dB}} = 10 log_{10}{\mathcal{X}} \sim \mathcal{N}(0,\sigma_{\text{dB}}^2)$.

Alternatively, some use a model where $P_r = P_t \Psi$ where $ \psi_{\text{dB}} = 10 log_{10}{\Psi}  \sim \mathcal{N}(PL_{\text{dB}}(d),\sigma_{\text{dB}}^2)$ for some \gls{PL} model.

\subsection*{Shadowing example}
Imagine a scenario in which we wish to evaluate Wi-Fi coverage for a desired range of $100$ m, with a minimum $SNR = 5$ dB and outage constraint at $1\%$ for the $5$ GHz frequencies. The \gls{PL} is modeled as exponential with $\alpha = 3$, $K = K_0 = -50$ dB (for $F_c \approx 5$ GHz), no TX and RX gain, a noise power of $P_n = -100$ dBm and a shadowing standard deviation of $\sigma_{\text{dB}} = 6$. What is the mimum transmition power to meet the outage constraint?
\\
\\
Answer:

\begin{align}
  SNR             & = \frac{P_r}{P_t} \geq 5 \text{ dB} \nonumber                                       \\
  P_r             & \geq -95 \text{ dB} \nonumber                                                       \\
  P_r             & = P_{t,\text{dB}} + K_{0,\text{dB}} + x_{\text{dB}} - \alpha 10 log_{10}d \nonumber \\
  P_{t,\text{dB}} & \geq -95 + 50 - x_{\text{dB}} + 60 \nonumber                                        \\
  P_{t,\text{dB}} & \geq 15 - x_{\text{dB}} \nonumber
\end{align}

Since $x_{\text{dB}}$ is normally distributed, we simply use the CDF of a Gaussian distribution to evaluate transmit power that would allow for the required outage constraint of $0.01$:

\begin{align}
  P(P_{t,\text{dB}} \geq  15 - x_{\text{dB}}) = 1 - 0.01 \nonumber \\
  15 - P_{t,\text{dB}} = \sigma_{\text{dB}}Q^{-1}(0.99) \nonumber  \\
  P_{t,\text{dB}} \geq 29 \text{ dBm} \nonumber
\end{align}

\chapter{Multipath Channel Models}

\glsaddall
\printglossary[type=\acronymtype,title=Acronyms]

% \bibliographystyle{ieeetran}
% \bibliography{ref}
\end{document}
